ms_figures

### 2024-05-02 ms_figures.Rmd
fixed height of fig 3 for fig3b y axis
figures fit A4 page restrictions

marine_cap_stacked_bar <- marine_cap_sciname %>%
  mutate(common_name = case_when(
    common_name == "alaska pollock(=walleye poll.)" ~ "alaska pollock",
    common_name == "ray-finned fishes" ~ "ray finned fishes",
    TRUE ~ common_name
  )) %>%
  mutate(common_name = gsub(" ", "\n", common_name)) %>%
  mutate(common_name = reorder(common_name, desc(total))) %>%
  ggplot(aes(x = consumption_live_t/consumption_live_magnitude, y = flow, fill = region)) +
  geom_bar(stat = "identity", position = "stack", width = 0.8) +
  scale_fill_manual(values = region6_palette) +
  labs(x = "", y = "") +
  lims(x = c(stacked_bar_min, stacked_bar_max)) +
  facet_grid(vars(common_name), switch = "y") +
  theme_minimal() +
  theme(
    strip.text.y.left = element_text(size = 8),
    strip.placement = "outside",
    legend.position = "none",
    panel.spacing = unit(2, "mm"),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    # axis.text.y = element_text(size = 8),
    plot.margin = unit(c(0, 5, -5, -10), "mm")
  )

@@

marine_aqua_stacked_bar <- marine_aqua_sciname %>%
  mutate(common_name = gsub(" ", "\n", common_name))%>%
  mutate(common_name = reorder(common_name, desc(total))) %>%
  ggplot(aes(x = consumption_live_t/consumption_live_magnitude, y = flow, fill = region)) +
  geom_bar(stat = "identity", position = "stack", width = 0.8) +
  scale_fill_manual(values = region6_palette) +
  labs(x = "", y = "") +
  lims(x = c(stacked_bar_min, stacked_bar_max)) +
  facet_grid(vars(common_name), switch = "y") +
  theme_minimal() +
  theme(
    strip.text.y.left = element_text(size = 8),
    strip.placement = "right",
    legend.position = "none",
    panel.spacing = unit(2, "mm"),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    plot.margin = unit(c(0, 5, -5, -10), "mm")
  )

@@

inland_cap_stacked_bar <- inland_cap_sciname %>%
  mutate(common_name = gsub(" nei", "", common_name)) %>%
  mutate(common_name = case_when(
    common_name == "ray-finned fishes" ~ "ray finned fishes",
    common_name == "freshwater siluroids" ~ "\nfreshwater siluroids",
    common_name == "nile perch" ~ "\nnile perch",
    TRUE ~ common_name
  )) %>%
  mutate(common_name = gsub(" ", "\n", common_name)) %>%
  mutate(common_name = reorder(common_name, desc(total))) %>%
  ggplot(aes(x = consumption_live_t/consumption_live_magnitude, y = flow, fill = region)) +
  geom_bar(stat = "identity", position = "stack", width = 0.8) +
  scale_fill_manual(values = region6_palette) +
  labs(x = "", y = "") +
  lims(x = c(stacked_bar_min, stacked_bar_max)) +
  facet_grid(vars(common_name), switch = "y") +
  theme_minimal() +
  theme(
    strip.text.y.left = element_text(size = 8),
    strip.placement = "outside",
    legend.position = "none",
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    panel.spacing = unit(2, "mm"),
    plot.margin = margin(r = 5, l=-10, b=-5, unit="mm")# unit(c(, 5, 0, -10), "mm")
  )

@@

inland_aqua_stacked_bar <- inland_aqua_sciname %>%
  mutate(common_name = gsub(" nei", "", common_name)) %>%
  mutate(common_name = case_when(
    common_name == "ray-finned fishes" ~ "ray finned fishes",
    common_name == "striped catfish" ~ "\nstriped catfish",
    common_name == "freshwater siluroids" ~ "\nfreshwater siluroids",
    common_name == "nile tilapia" ~ "\nnile tilapia",
    TRUE ~ common_name
  )) %>%
  mutate(common_name = gsub(" ", "\n", common_name)) %>%
  mutate(common_name = reorder(common_name, desc(total))) %>%
  mutate(region = case_when(
    region == "North America" ~ "N. America",
    region == "South America" ~ "S. America",
    TRUE ~ region
  )) %>%
  ggplot(aes(x = consumption_live_t/consumption_live_magnitude, y = flow, fill = region)) +
  geom_bar(stat = "identity", position = "stack", width = 0.8) +
  scale_fill_manual(values = region6_palette) +
  labs(x = "", y = "", fill = "") +
  lims(x = c(stacked_bar_min, stacked_bar_max)) +
  facet_grid(vars(common_name), switch = "y") +
  theme_minimal() +
  theme(
    strip.placement = "outside",
    strip.text.y.left = element_text(size = 8),
    legend.position = "bottom",
    legend.box = "horizontal",
    legend.text = element_text(size = 8),
    legend.key.size = unit(3, "mm"),
    legend.box.margin = margin(l = -25, unit = "mm"),
    legend.margin = margin(t = -7, b = 0, unit = "mm"),
    panel.spacing = unit(2, "mm"),
    plot.margin = unit(c(0, 5, 0, -10), "mm")
  )

@@

# ggsave(file.path(outdir, "fig2.png"), width = 9, height = 13, dpi = 500, unit = "in", device = "png")
ggsave(file.path(outdir, "fig2.pdf"), width = 180, height = 320, unit = "mm", device = "pdf")
```

@@

# ggsave(file.path(outdir, "fig3.png"))
ggsave(file.path(outdir, "fig3.pdf"), height = 180, width = 180, unit = "mm", device = "pdf")
```

>>>>

marine_cap_stacked_bar <- marine_cap_sciname %>%
  mutate(common_name = case_when(
    common_name == "alaska pollock(=walleye poll.)" ~ "alaska pollock",
    common_name == "ray-finned fishes" ~ "ray finned fishes",
    TRUE ~ common_name
  )) %>%
  mutate(common_name = gsub(" ", "\n", common_name)) %>%
  mutate(common_name = reorder(common_name, desc(total))) %>%
  ggplot(aes(x = consumption_live_t/consumption_live_magnitude, y = flow, fill = region)) +
  geom_bar(stat = "identity", position = "stack", width = 0.7) +
  scale_fill_manual(values = region6_palette) +
  labs(x = "", y = "") +
  lims(x = c(stacked_bar_min, stacked_bar_max)) +
  facet_grid(vars(common_name), switch = "y") +
  theme_minimal() +
  theme(
    strip.text.y.left = element_text(size = 8),
    strip.placement = "outside",
    legend.position = "none",
    panel.spacing = unit(0.5, "mm"),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    # axis.text.y = element_text(size = 8),
    plot.margin = unit(c(0, 5, -5, -10), "mm")
  )

@@

marine_aqua_stacked_bar <- marine_aqua_sciname %>%
  mutate(common_name = gsub(" ", "\n", common_name))%>%
  mutate(common_name = reorder(common_name, desc(total))) %>%
  ggplot(aes(x = consumption_live_t/consumption_live_magnitude, y = flow, fill = region)) +
  geom_bar(stat = "identity", position = "stack", width = 0.7) +
  scale_fill_manual(values = region6_palette) +
  labs(x = "", y = "") +
  lims(x = c(stacked_bar_min, stacked_bar_max)) +
  facet_grid(vars(common_name), switch = "y") +
  theme_minimal() +
  theme(
    strip.text.y.left = element_text(size = 8),
    strip.placement = "right",
    legend.position = "none",
    panel.spacing = unit(0.5, "mm"),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    plot.margin = unit(c(0, 5, -5, -10), "mm")
  )

@@

inland_cap_stacked_bar <- inland_cap_sciname %>%
  mutate(common_name = gsub(" nei", "", common_name)) %>%
  mutate(common_name = case_when(
    common_name == "ray-finned fishes" ~ "ray finned fishes",
    common_name == "freshwater siluroids" ~ "\nfreshwater siluroids",
    common_name == "nile perch" ~ "\nnile perch",
    TRUE ~ common_name
  )) %>%
  mutate(common_name = gsub(" ", "\n", common_name)) %>%
  mutate(common_name = reorder(common_name, desc(total))) %>%
  ggplot(aes(x = consumption_live_t/consumption_live_magnitude, y = flow, fill = region)) +
  geom_bar(stat = "identity", position = "stack", width = 0.7) +
  scale_fill_manual(values = region6_palette) +
  labs(x = "", y = "") +
  lims(x = c(stacked_bar_min, stacked_bar_max)) +
  facet_grid(vars(common_name), switch = "y") +
  theme_minimal() +
  theme(
    strip.text.y.left = element_text(size = 8),
    strip.placement = "outside",
    legend.position = "none",
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    panel.spacing = unit(0.5, "mm"),
    plot.margin = margin(r = 5, l=-10, b=-5, unit="mm")# unit(c(, 5, 0, -10), "mm")
  )

@@

inland_aqua_stacked_bar <- inland_aqua_sciname %>%
  mutate(common_name = gsub(" nei", "", common_name)) %>%
  mutate(common_name = case_when(
    common_name == "ray-finned fishes" ~ "ray finned fishes",
    common_name == "striped catfish" ~ "\nstriped catfish",
    common_name == "freshwater siluroids" ~ "\nfreshwater siluroids",
    common_name == "nile tilapia" ~ "\nnile tilapia",
    TRUE ~ common_name
  )) %>%
  mutate(common_name = gsub(" ", "\n", common_name)) %>%
  mutate(common_name = reorder(common_name, desc(total))) %>%
  mutate(region = case_when(
    region == "North America" ~ "N. America",
    region == "South America" ~ "S. America",
    TRUE ~ region
  )) %>%
  ggplot(aes(x = consumption_live_t/consumption_live_magnitude, y = flow, fill = region)) +
  geom_bar(stat = "identity", position = "stack", width = 0.7) +
  scale_fill_manual(values = region6_palette) +
  labs(x = "", y = "", fill = "") +
  lims(x = c(stacked_bar_min, stacked_bar_max)) +
  facet_grid(vars(common_name), switch = "y") +
  theme_minimal() +
  theme(
    strip.placement = "outside",
    strip.text.y.left = element_text(size = 8),
    legend.position = "bottom",
    legend.box = "horizontal",
    legend.text = element_text(size = 8),
    legend.key.size = unit(3, "mm"),
    legend.box.margin = margin(l = -25, unit = "mm"),
    legend.margin = margin(t = -7, b = 0, unit = "mm"),
    panel.spacing = unit(0.5, "mm"),
    plot.margin = unit(c(0, 5, 0, -10), "mm")
  )

@@

# ggsave(file.path(outdir, "fig2.png"), width = 9, height = 13, dpi = 500, unit = "in", device = "png")
ggsave(file.path(outdir, "fig2.pdf"), width = 180, height = 295, unit = "mm", device = "pdf")
```

@@

# ggsave(file.path(outdir, "fig3.png"))
ggsave(file.path(outdir, "fig3.pdf"), height = 210, width = 180, unit = "mm", device = "pdf")
```
